
loading the libraries that will be used in the project
```{r, echo=FALSE}
library(caret)
library(plyr)
library(dplyr)
library(C50)
library(mlbench)

```

Reading the train and test dataset
```{r, echo=FALSE}
trainingOrigin<-read.csv("pml-training.csv")
testingOrigin<-read.csv("pml-testing.csv")

```

dealing with the train data. Spliting the train data into test and train
```{r, echo=FALSE}
set.seed(20497)
inTrain<-createDataPartition(y=trainingOrigin$classe,p=0.70,list=FALSE)
training<-trainingOrigin[inTrain,]
testing<-trainingOrigin[-inTrain,]
```

## Data Processing
Checking the null variables and dealing with the null variables
```{r, echo=FALSE}
na_columns <- names(training[,colSums(is.na(training)) > 0])
length(na_columns)

columns_to_remove_1 <-
  grep("avg|var|stddev|max|min|amplitude|kurtosis|skewness",
       names(training))
length(columns_to_remove_1)

```

Creating the clean training dataset that will be used onwards
```{r, echo=FALSE}
training_1 <- training[,!names(training) %in% c("V1","user_name",
                                                "raw_timestamp_part_1",
                                                "raw_timestamp_part_2","cvtd_timestamp",
                                                "new_window", "num_window",
                                                names(training[,columns_to_remove_1]))]
dim(training_1)

ncol(training_1)
```

removing the index column and applying cross validation
```{r, echo=FALSE}
forSizes <- c(1:10, 15, 20, 25, 30, 35, 40, 50, 52)
control <- rfeControl(functions=rfFuncs, method="cv", number=10)
training_1 <- training_1[ , -1]
control <- trainControl(method="cv", number=10)
```

using different models to train the dataset to allow selection of the best model.
```{r, echo=FALSE}
set.seed(12345)
ctmodFit<-train(classe~.,data=training_1,method="rpart",trControl=control)

set.seed(12345)
rfmodFit<-train(classe~.,data=training_1,method="rf",PROX=TRUE, trControl=control)

set.seed(12345)
bomodFit<-train(classe~.,data=training_1,method="gbm", trControl=control,verbose=FALSE)

set.seed(12345)
c5modFit<-train(classe~.,data=training_1,method="C5.0", trControl=control,verbose=FALSE)

```

resampling the models and produce summary with the plot representation
```{r, echo=FALSE}
results<-resamples(list(RPART=ctmodFit, RF=rfmodFit, GBM=bomodFit, C5=c5modFit))
summary(results)

topresults<-resamples(list(RF=rfmodFit, GBM=bomodFit, C5=c5modFit))
bwplot(topresults)

```

fitting the best model which is C5 and make the prediction required for the 20 samples.
```{r, echo=FALSE}
c5Grid<-expand.grid(trials=20, model="rules", winnow=TRUE)
c5modFitFull<-train(classe ~ ., data=training_1, method="C5.0", verbose=FALSE, tuneGrid=c5Grid)


c5predictOriginTest<-predict(c5modFitFull,testingOrigin)
c5predictOriginTest

```


